A Real-Time Sonar Simulator for Automatic Target Recognition

### 2016-08-30 Simulator/article.tex
la2pdf commit - 2016:08:04	20:15:01	(to. 4.aug.)
la2pdf commit - 2016:08:30	10:50:10	(ti.30.aug.)

>>>>

\begin{figure*}[!tbp]\centering%
\graphicsAI[width=\linewidth]{gfx/fig_images_sonar_simulation.pdf}%
\label{fig_sonar_simulation}%
\caption{SAS images of 2 cylinders and a torpedo located in the Jesus Bay, Norway. These detections are just 3 objects out of 1000+ detected in this run.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\graphicsAI[width=\linewidth]{gfx/fig_rocs.pdf}%
\label{fig_sonar_simulation}%
\caption{Receiver operating characteristics curves.}
\end{figure*}

\begin{figure*}[!tbp]\centering%
\subfloat[SAS images of 2 cylinders and a torpedo.]{%
\graphicsAI[width=0.5\linewidth]{gfx/fig_images_sonar_simulation.pdf}%
\label{fig_sonar_simulation}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}
